Supplements for ``Tensor denoising and completion based on ordinal observations''

### 2020-02-04 ICML/miaoyan/ordinalT_supp_v2.tex
Update ordinalT_supp_v2.tex

\section{Convexity of the likelihood function}
\begin{thm}\label{thm:convexity}
\begin{align}
 \logl(\Theta, \mb)&=\sum_{\omega\in\Omega}\sum_{\ell\in[L]} \Big\{\mathds{1}_{\{y_\omega=\ell\}} \log \big[f(\theta_\omega+b_\ell)-  f(\theta_\omega+b_{\ell-1})\big]\Big\}, \text{ where } f(x) = \frac{e^x}{1+e^x}.
 \end{align}
is a concave function to $(\Theta,\mb)$
\end{thm}
\begin{proof}
We use $(\Theta,\mb)$ abusively as $(Vec(\Theta)^T,\mb^T)^T$ in this proof.
Let us denote $\lambda(u,v) = \log \big[f(u)-  f(v)\big]$.
It is enough to show that $\lambda(u,v)$
is a concave function to $(u,v)$ where $u>v$. Because if $\lambda(u,v)$ is a concave function and $u,v$ are both linear functions of $(\Theta,\mb) $ such that
$$u = \ma_1^T(\Theta,\mb), v = \ma_2^T(\Theta,\mb) \text{ for some }\ma_1,\ma_2\in \mathbb{R}^{d_{\text{total}}+L-1},$$ then $\lambda(u,v) = \lambda(\ma_1^T(\Theta,\mb),\ma_2^T(\Theta,\mb)))$ is a concave function to $(\Theta,\mb)$
by the definition of the convexity. Furthermore, we can conclude that $\logl(\Theta, \mb) $ is a concave function to $(\Theta,\mb)$ because $\logl(\Theta, \mb)$
can be written as the form of summations of $\lambda(u,v)$. To prove the convexity of $\lambda(u,v)$, we have the following.
\begin{equation*}
\lambda(u,v) = \log\big[f(u)-f(v)\big]=\log\big[\int\mathds{1}_{(u,v)}(x)f'(x)dx\big].
\end{equation*}
Notice that  $\mathds{1}_{(u,v)}(x)$ is log-concave to $(u,v,x)$ and $f'(x)$ is log-concave to $x$ because $f'(x) = \frac{e^x}{(1+e^x)^2}$. Those convexities imply that $\mathds{1}_{(u,v)}(x)f'(x)$
is a log-concave function to $(u,v,x)$. Therefore, we can conclude that the $\lambda(u,v)$ is a concave function from the lemma~\ref{lem:convexity}.
\end{proof}

\begin{lem}[Corollary 3.5 in~\cite{brascamp2002extensions}]\label{lem:convexity}
Let $F(x,y):\mathbb{R}^{m+n}\rightarrow \mathbb{R}$ be an integrable function where $x\in \mathbb{R}^{m},y\in \mathbb{R}^n$. Let $$G(x) = \int_{\mathbb{R}^n}F(x,y)dy.$$ If $F(x,y)$ is a log concave function to (x,y), then $G(x)$ is a log concave function.
\end{lem}

>>>>

\section{Convexity of the likelihood function}
\begin{thm}\label{thm:convexity}
\begin{align}
 \logl(\Theta, \mb)&=\sum_{\omega\in\Omega}\sum_{\ell\in[L]} \Big\{\mathds{1}_{\{y_\omega=\ell\}} \log \big[f(\theta_\omega+b_\ell)-  f(\theta_\omega+b_{\ell-1})\big]\Big\}, \text{ where } f(x) = \frac{e^x}{1+e^x}.
 \end{align}
is a concave function to $(\Theta,\mb)$
\end{thm}
\begin{proof}
We use $(\Theta,\mb)$ abusively as $(Vec(\Theta)^T,\mb^T)^T$ in this proof.
Let us denote $\lambda(u,v) = \log \big[f(u)-  f(v)\big]$.
It is enough to show that $\lambda(u,v)$
is a concave function to $(u,v)$ where $u>v$. Because if $\lambda(u,v)$ is a concave function and $u,v$ are both linear functions of $(\Theta,\mb) $ such that
$$u = \ma_1^T(\Theta,\mb), v = \ma_2^T(\Theta,\mb) \text{ for some }\ma_1,\ma_2\in \mathbb{R}^{d_{\text{total}}+L-1},$$ then $\lambda(u,v) = \lambda(\ma_1^T(\Theta,\mb),\ma_2^T(\Theta,\mb)))$ is a concave function to $(\Theta,\mb)$
by the definition of the convexity. Furthermore, we can conclude that $\logl(\Theta, \mb) $ is a concave function to $(\Theta,\mb)$ because $\logl(\Theta, \mb)$
can be written as the form of summations of $\lambda(u,v)$. To prove the convexity of $\lambda(u,v)$, we have the following.
\begin{equation*}
\lambda(u,v) = \log\big[f(u)-f(v)\big]=\log\big[\int\mathds{1}_{(u,v)}(x)f'(x)dx\big].
\end{equation*}
Notice that  $\mathds{1}_{(u,v)}(x)$ is log-concave to $(u,v,x)$ and $f'(x)$ is log-concave to $x$ because $f'(x) = \frac{e^x}{(1+e^x)^2}$. Those convexities imply that $\mathds{1}_{(u,v)}(x)f'(x)$
is a log-concave function to $(u,v,x)$. Therefore, we can conclude that the $\lambda(u,v)$ is a concave function from the lemma~\ref{lem:lossconvexity}.
\end{proof}

\begin{lem}[Corollary 3.5 in~\cite{brascamp2002extensions}]\label{lem:lossconvexity}
Let $F(x,y):\mathbb{R}^{m+n}\rightarrow \mathbb{R}$ be an integrable function where $x\in \mathbb{R}^{m},y\in \mathbb{R}^n$. Let $$G(x) = \int_{\mathbb{R}^n}F(x,y)dy.$$ If $F(x,y)$ is a log concave function to (x,y), then $G(x)$ is a log concave function.
\end{lem}
